\bf Is this normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-04 paper.qmd
finished the early example

For example, @fit-compare compares a new sample of patient scores against the normal range represented by an ellipse.

@@

![Sample of patients relative to confidence ellipse.](images/example1.png){#fig-compare1 width=300 align="center"}

![Sample of patients relative to relative to simulated sample of normal patients.](images/example2.png){#fig-compare width=300 align="center"}

Illustration of current procedure: (a) compare new sample with points of the surface of a $p-D$ ellipse, (b) compare new sample with a simulated sample of normal patients. Although both approaches are useful, the rough edges of the projected ellipse points makes it difficult to precisely assess the positions of the new sample against the normal bounds.
:::

>>>>

For example, @fig-compare compares a new sample of patient scores against the normal range represented by an ellipse (a) and also against a simulated sample of normal patients (b). While these are useful approaches, the ragged edges of the projected ellipse make it difficult to compare the new sample precisely agains the normal ranges.

@@

![Relative to confidence ellipse.](images/example1.png){#fig-compare1 width=250 align="center"}

![Relative to normal patients.](images/example2.png){#fig-compare width=250 align="center"}

Illustration of current procedure: (a) compare new sample with points of the surface of a $p\text{-}D$ ellipse, (b) compare new sample with a simulated sample of normal patients. Although both approaches are useful, the rough edges of the projected ellipse points makes it difficult to precisely assess the positions of the new sample against the normal bounds.
:::

### 2024-07-04 paper.tex
finished the early example

\textless PLOTS FROM USCHI's PHYSICS EXAMPLE HERE\textgreater{}

>>>>

For example, Figure~\ref{fig-compare} compares a new sample of patient
scores against the normal range represented by an ellipse (a) and also
against a simulated sample of normal patients (b). While these are
useful approaches, the ragged edges of the projected ellipse make it
difficult to compare the new sample precisely agains the normal ranges.

\includegraphics[width=2.60417in,height=\textheight]{images/example1.png}

\subcaption{\label{fig-compare1}Relative to confidence ellipse.}

\includegraphics[width=2.60417in,height=\textheight]{images/example2.png}

\subcaption{\label{fig-compare}Relative to normal patients.}

\caption{\label{fig-compare}Illustration of current procedure: (a)
compare new sample with points of the surface of a \(p\text{-}D\)
ellipse, (b) compare new sample with a simulated sample of normal
patients. Although both approaches are useful, the rough edges of the
projected ellipse points makes it difficult to precisely assess the
positions of the new sample against the normal bounds.}
